### 2014-10-31 implementation.tex
edits

Figure~\ref{fig:impl_mod} describes the overall system architecture. The main
idea in our implementation of \name is to offload the majority of concerns
related to data management such as replication, fault tolerance, availability
and convergence to Cassandra, an off-the-shelf eventually consistent store
(called \emph{backing store} in the sequel). Replicated data type
implementation and the stronger consistency semantics are enforced in the
\emph{shim layer}. Our implementation supports eventual, causal and strong
consistency for operations, and RC, MAV and RR transaction semantics. All of
this functionality is implemented on top of the standard interface exposed by
Cassandra, and illustrates the portability of \name programming model. Complex
business logic is implemented with the help of transactions on the server side,
with clients interacting with the web-service over REST interface.

>>>>

\name is implemented as a shallow extension of Haskell on the Glasgow Haskell
Compiler (GHC). We utilize Template Haskell functionality to implemement static
contract classification. Our proof obligations are discharged automatically
with the help of Z3~\cite{} SMT solver. Figure~\ref{fig:impl_mod} describes the
overall system architecture. The main idea in our implementation of \name is to
offload the majority of concerns related to data management such as
replication, fault tolerance, availability and convergence to Cassandra, an
off-the-shelf eventually consistent store (called \emph{backing store} in the
sequel).

Replicated data type implementation and the stronger consistency semantics are
enforced in the \emph{shim layer}. Our implementation supports eventual, causal
and strong consistency for operations, and RC, MAV and RR transaction
semantics. All of this functionality is implemented on top of the standard
interface exposed by Cassandra, and illustrates the portability of \name
programming model. Complex business logic is implemented with the help of
transactions on the server side, with clients interacting with the web-service
over REST interface. From an engineering perspective, resorting to an
off-the-shelf backing store meant that our entire implementation comprised of
only around 2500 lines of Haskell code, which is packaged as a Haskell library.
